---
title: "Exercices Lecture 4"
author: "Paolo Crosetto"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# creating tidy data: reshape with `gather()` and `spread()`

## Exercice 1

> 

```{r ex1}

  
```

## Exercice 2

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex2}

  
```


## Exercice 3

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```

## Exercice 1

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```

## Exercice 1

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```

## Exercice 1

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```

## Exercice 1

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```

## Exercice 1

> tidy world_bank_pop dataset so that 'year' is a variable and for each country and each year you have urban population and urban population growth only. Plot as a geom_line the total population for each country over the years.

```{r ex1}

  
```




